\section{ALDRIDGE}

\textbf{First Generation}

The first Aldridge we know of was \uppercase{Edward Henry Aldridge} who married \uppercase{Leah North} in 1789 at St Martin in the Fields, London. They had five children: Judith Aldridge, Virginia Aldridge, Leah North Aldridge, \uppercase{Napoleon Aldridge}, (who was \uppercase{Ralph Munday Denton Barker}'s great grandfather), and Edward Henry Aldridge. 

\textsc{Judith Aldridge} was christened on 14 February 1794 at St. Georges,	Bloomsbury, Middlesex.

\textsc{Virginia Aldridge} was born in 1796 in Chelsea, Middlesex, and christened on 9 August 1796 at St Mary Magdalene,  	Bermondsey. She married  (first name unknown) Calvert and they had three daughters, Leah Calvert (b.1825), Judith Calvert(b.1829) and Virginia Calvert (b.1831). In April 1851 in	Hunslet, Yorkshire, she was listed as being a Shopkeeper and was a widow.

\textsc{Leah North Aldridge} was born in London but christened at the University Church, St Mary the Virgin, in Oxford on 16 April 1802. She married Joseph Lee in Epsom, Surrey, and they had two children.

All that is known of \textsc{Edward Henry Aldridge} is that he was married twice, and had three daughters and one son from the first marriage,  with no issue from the second. 

\textbf{Second Generation}

\uppercase{Napoleon Aldridge} was born in 1801 and married \uppercase{Mary Ann Chymist} on 1 April 1832 at St. Giles in the Fields, Camden.  They had eight children: Edward Henry Aldridge, Napoleon Alfred Aldridge, Leah North Aldridge, Virginia Elizabeth Aldridge, William Aldridge, Alice Judith Aldridge, Alfred Frank Aldridge and \uppercase{Catherine Aldridge}, (who was \uppercase{Ralph Munday Denton Barker}'s maternal grandmother).

\textsc{Edward Henry Aldridge} was born on 26 August 1832 in Middlesex. He married Emma Ryan on 2 May 1858, and they had five children: Edward Henry Aldridge (b.1859), Marian Emma Aldridge (b.1862), William Ernest Aldridge (b.1865), Emma Annie Aldridge (b.1866), and Percy Leopold Aldridge (b.1870). He was a Clerk and then solicitor in the Masters Office, Queens Bench in London. He died on 24 December 1899 and was buried at Highgate Cemetery.

\textsc{Napoleon Alfred Aldridge} was born on 20 January 1836 in Middlesex, and married Jane Maria Staples on 15 May 1865. They had ten children: Alfred Frank Aldridge (b.1866), Herbert Aldridge (b.1867), Walter Napoleon Aldridge (b.1869), Sidney Aldridge (b.1871), Amelia Jane Alice Aldridge (b.1872), Arthur William Staples Aldridge (b.1874), Roland George Aldridge (b.1879), Kate Edith Aldridge (b.1881), Harriet Mabel Aldridge (b.1884), and Newton Aldridge (b.1889).  Like his older brother, he was a clerk in the Masters Office of the Queens Bench. He died on 12 December 1905 and was buried in Honor Oak Cemetery.

\textsc{Leah North Aldridge} was born on 11 December 1837 in Middlesex, and married William George Cooper on 11 July 1868. They had two children, Jesse Amelia Letitia Cooper (b.1875) and George Aldridge Cooper (b.1893). She died on	20 April 1912 and was buried at Highgate Cemetery.

\textsc{Virginia Elizabeth Aldridge} was born on 4 December 1839 in	Middlesex, and married William John Abram on 24 August 1862. They had one child: Alice Lily Abram (b.1864). She died on 25 March 1912.

\textsc{William Aldridge} was born on 27 February 1843 in	Islington. In 1871 he was a farmer with 16 acres in	Sutton, Surrey (perhaps looking after his father's land).

\textsc{Alice Judith Aldridge} was born on 4 January 1845 in	Islington, and married Edward Hall on 29 December 1881.  

\textsc{Alfred Frank Aldridge} was born on 23 May 1846 in Islington, Middlesex, and married Laura Palmer on 21 June 1877. They had two children:  Mary Aldridge (b.1878) and Wallis Aldridge (b.1881). He was a solicitor.




